### 2014-08-08 paper/paper.tex
Fixed the table labels. Changed the download instructions

Draft 5 %TODO ditch this

@@

%TODO change the label names

The following experiments examine the results of the Maximum Entropy classifier
and the Naive Bayes classifier with various feature selection methods turned on
or off. The `Baseline' experiment refers to no feature selection. The `Just
Stopwords' experiment refers the only removing stopwords. The `Just Uncommon'
experiment refers to only removing words with a document frequency of one. The
`Just Normalization' experiment refers to only applying feature normalization
mechanisms. The `All' experiment refers to testing the classifier with all of
the previous feature selection methods turned on.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|}
        \hline
        Description        & Positive & Neutral & Negative & Overall \\
        \hline
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment.}
    \label{table:numfeatures}
\end{table}

@@

%TODO finish accuracy

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline       & 48.37   & 2.15 & -     & & \\
        Just Stopwords & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
        Just Uncommon  & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
        Just Normalize & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
        All            & \textbf{50.96} & 1.93 &  2.59 & \textbf{63.82} & 0.91 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

As Table \ref{table:maxent-results} shows, the `All' experiment provides the
best results over the baseline. The `Just Stopwords' experiment actually
provides slightly worse results then the baseline indicating that in context of
Tweets with so few features in each example every feature counts. The `Just
Uncommon' experiment does not provide very significant gains when used alone.
This is potentially due to the fact that without normalization turned,
features such as `just' are `Just' are determined to be different and may be
removed if each only occur once.

@@

% TODO make serif?

@@

%TODO finish table

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline       & 48.11  & 0.74 & - & & \\
        Just Stopwords & 47.29  & 0.76 & -0.82 & & \\
        Just Uncommon  & 48.34  & 1.11 &  0.23 & & \\
        Just Normalize & \textbf{49.44} & 1.00 & 1.33 & & \\
        All            & 49.28  & 0.81 &  1.17 & & \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        UoM        & 51.81 \\
        \textbf{MaxEnt}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
%TODO add naive bayes

@@

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip -O tsent.zip
unzip tsent.zip
cd tsent
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\footnotesize]
        a
        about
        an
        are
        as
        at
        be
        by
        com
        for
        from
        how
        in
        is
        it
        of
        on
        or
        that
        the
        this
        to
        was
        what
        when
        where
        who
        will
        with
\end{Verbatim}

>>>>

@@

The following experiments examine the results of the Maximum Entropy classifier
and the Naive Bayes classifier with various feature selection methods turned on
or off. The `Baseline' experiment refers to no feature selection. The `Only
Stopword Removal' experiment refers the only removing stopwords as feature
selection. The `Only Rare Word Removal' experiment refers to only removing
words with a document frequency of 1. The `Only Normalization' experiment
refers to only applying feature normalization mechanisms. The `All Feature
Selection' experiment refers to testing the classifier with all of the previous
feature selection methods turned on.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|}
        \hline
        Description            & Positive & Neutral & Negative & Overall \\
        \hline
        Baseline               & 20.65    & 20.45   & 20.96    & 20.58 \\
        Only Stopword Removal  & 17.13    & 16.86   & 17.41    & 17.04 \\
        Only Rare Word Removal & 18.43    & 17.87   & 18.85    & 18.21 \\
        Only Normalization     & 19.65    & 19.16   & 20.06    & 19.46 \\
        All Feature Selections & 14.85    & 14.06   & 15.10    & 14.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment.}
    \label{table:numfeatures}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline               & 48.37   & 2.15 &     - & \textbf{63.89} & 1.13 \\
        Only Stopword Removal  & 48.27   & 1.83 & -0.10 & 62.07 & 1.69 \\
        Only Rare Word Removal & 49.02   & 1.96 &  0.65 & 62.47 & 1.91 \\
        Only Normalization     & 49.55   & 2.10 &  1.18 & 63.57 & 1.75 \\
        All Feature Selections & \textbf{50.96}  & 1.93  &  2.59 & 63.82 & 0.91 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

As Table \ref{table:maxent-results} shows, the `All Feature Selections'
experiment provides the best results over the baseline. The `Only Stopword
Removal' experiment actually provides slightly worse results then the baseline
indicating that in context of Tweets with so few features in each example every
feature counts. The `Only Rare Words Removal ' experiment does not provide very
significant gains when used alone.  This is potentially due to the fact that
without normalization turned, features such as `just' are `Just' are determined
to be different and may be removed if each only occur once.

@@

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ & $\mu Acc$ & $\sigma Acc$ \\
        \hline
        Baseline               & 48.11  & 0.74 & -     & 53.13 & 1.48 \\
        Only Stopword Removal  & 47.29  & 0.76 & -0.82 & 52.71 & 1.16 \\
        Only Rare Word Removal & 48.34  & 1.11 &  0.23 & 53.92 & 1.32 \\
        Only Normalization     & \textbf{49.44} & 1.00 & 1.33 & \textbf{55.92} & 0.99 \\
        All Feature Selections & 49.28  & 0.81 &  1.17 & 54.91 & 1.05 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

As Table \ref{table:bayes-results} and Figure \ref{figure:bayes} indicates both
removing stopwords and removing rare words appear to negatively affect
performance of the naive bayes classifier.

@@

\begin{table}[H]
    \begin{center}
        \small
    \begin{tabular}{|r|l|}
        \hline
        Team            & F \\
        \hline
        NRC-Canada      & 69.02 \\
        GU-MLT-LT       & 65.27 \\
        teragram        & 64.86 \\
        BOUNCE*         & 63.53 \\
        KLUE*           & 63.06 \\
        AMI\&ERIC       & 62.55 \\
        FBM             & 61.17 \\
        AVAYA           & 60.84 \\
        SAIL*           & 60.14 \\
        UT-DB           & 59.87 \\
        FBK-irst        & 59.76 \\
        nlp.cs.aueb.gr  & 58.91 \\
        UNITOR          & 58.27 \\
        LVIC-LIMSI      & 57.14 \\
        Unigon          & 56.96 \\
        NILC\_USP       & 56.31 \\
        DataMining      & 55.52 \\
        ECNUCS          & 55.05 \\
        nlp.cs.aueb.gr  & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP        & 54.33 \\
        CodeX           & 53.89 \\
        Oasis           & 53.84 \\
        NTNU            & 53.23 \\
        UoM             & 51.81 \\
        \textbf{MaxEnt} & \textbf{50.96} \\
        SSA-UO          & 50.17 \\
        SenselyticTeam  & 50.10 \\
        \textbf{Naive Bayes} & \textbf{49.44} \\
        \textit{9 more teams}&  \textless\ 49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers submitted to the SemEval-2013
        workshop. Sorted by F-score. * denotes other Maximum Entropy classifiers}
    \label{table:comparison}
\end{table}

@@

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip
unzip dist.zip
cd twitter-sentiment-dist
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\footnotesize]
         a                   of
         about               on
         an                  or
         are                 that
         as                  the
         at                  this
         be                  to
         by                  was
         com                 what
         for                 when
         from                where
         how                 who
         in                  will
         is                  with
         it
\end{Verbatim}
